Accelerated oblique random survival forests

### 2022-06-15 paper/jmlr/main.tex
paper edits
grouping all the RFs into axis based or oblique should make the paper's
main hypotheses easier to test.

Table \ref{table:1} is an example of a referenced \LaTeX{}. Several machine learning algorithms can engage with right-censored time-to-event outcomes. In the current study, we consider four classes of learners: random forests, boosting ensembles, regression models, and neural networks.

accelerated oblique random survival forests \texttt{aorsf}

original oblique random survival forests \texttt{obliqueRSF}

axis-based random survival forests \texttt{randomForestSRC \& ranger}

axis-based conditional inference forests \texttt{party}

gradient boosted decision trees \texttt{xgboost}

\begin{table}[h!]
\centering
\begin{tabular}{p{2cm} | p{3cm} p{7cm}}
 \hline
 Learner & Software & Description \\ [0.5ex]
 \hline\hline
 \multicolumn{3}{l}{\textit{Random Survival Forests}}\\
 \hline\hline
 Standard & \href{https://www.randomforestsrc.org/index.html}{\texttt{RandomForestSRC}} & Axis based survival trees following Leo Breiman's original random forest algorithm, with cut-points selected to maximize a log-rank statistic.  \\ \hline
 Oblique & \href{https://CRAN.R-project.org/package=obliqueRSF}{\texttt{obliqueRSF}} \newline \href{https://bcjaeger.github.io/aorsf/}{\texttt{aorsf}} & Oblique survival trees following Leo Breiman's random forest algorithm but not using random coefficients for linear combinations. \texttt{obliqueRSF} uses penalized models, and \texttt{aorsf} additionally uses partially trained models. Cut-points are selected to maximize a log-rank statistic. \\ \hline
 Extremely \,Randomized & \href{https://CRAN.R-project.org/package=ranger}{\texttt{ranger}} & Axis-based survival trees grown with randomly selected features and cut-points\\ \hline
 Conditional \,Inference & \href{http://party.r-forge.r-project.org/}{\texttt{party}} & Axis based survival trees grown using unbiased recursive partitioning.  \\
 \hline\hline
 \multicolumn{3}{l}{\textit{Boosting ensembles}}\\
 \hline\hline
 Trees & \href{https://xgboost.readthedocs.io/en/stable/#}{\texttt{xgboost}} & The Cox likelihood function is maximized additively with decision trees. Nested cross validation (5 folds) is applied to tune the number of trees grown.  \\
 Models & \href{https://xgboost.readthedocs.io/en/stable/#}{\texttt{xgboost}} & The accelerated failure time likelihood function is maximized additively with decision trees. Nested cross validation (5 folds) is applied to tune the number of trees grown.  \\
 \hline\hline
 \multicolumn{3}{l}{\textit{Regression models}}\\
 \hline\hline
 Cox Net & \texttt{glmnet} & The Cox model is fit using an elastic net penalty. Nested cross validation (5 folds) is applied to tune penalty terms.\\
 \hline\hline
 \multicolumn{3}{l}{\textit{Neural networks}}\\
 \hline\hline
 Cox Time & 6 & 87837  \\
 \hline
\end{tabular}
\caption{Table to test captions and labels.}
\label{table:1}
\end{table}

\section{Results}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\begin{longtable}{lcclccl}
\toprule
\multicolumn{3}{c}{ } & \multicolumn{4}{c}{Computing time, seconds} \\
\cmidrule(l{3pt}r{3pt}){4-7}
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Performance metric (SD)} & \multicolumn{2}{c}{Fit model} & \multicolumn{2}{c}{Predict risk} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7}
  & C-Statistic & Scaled Brier & Mean & Ratio & Mean & Ratio\\
\midrule
\endfirsthead
\multicolumn{7}{@{}l}{\textit{(continued)}}\\
\toprule
  & C-Statistic & Scaled Brier & Mean & Ratio & Mean & Ratio\\
\midrule
\endhead

@@

\hspace{1em}Party & 0.772 (0.058) & 0.076 (0.042) & 2.181 & 2.19 & 4.889 & 4.62\\
\hspace{1em}aORSF(i=1) & 0.755 (0.059) & 0.057 (0.055) & 0.998 & 1.00 & 1.057 & 1.00\\
\hspace{1em}Ranger & 0.754 (0.064) & 0.064 (0.027) & 0.397 & 0.398 & 0.510 & 0.483\\
\hspace{1em}aORSF(i=15) & 0.754 (0.063) & 0.052 (0.056) & 2.498 & 2.50 & 2.559 & 2.42\\
\hspace{1em}Rfsrc & 0.752 (0.064) & 0.061 (0.047) & 0.775 & 0.777 & 0.833 & 0.787\\
\hspace{1em}aorsf\_net & 0.750 (0.059) & 0.055 (0.064) & 28.449 & 28.5 & 28.510 & 27.0\\

@@

\hspace{1em}aORSF(i=15) & 0.764 (0.008) & 0.143 (0.016) & 11.867 & 2.56 & 12.403 & 2.43\\
\hspace{1em}Ranger & 0.756 (0.013) & 0.102 (0.017) & 0.555 & 0.120 & 0.724 & 0.142\\
\hspace{1em}Party & 0.753 (0.013) & 0.118 (0.016) & 8.030 & 1.73 & 10.445 & 2.05\\
\hspace{1em}aORSF(i=1) & 0.751 (0.002) & 0.120 (0.012) & 4.636 & 1.00 & 5.106 & 1.00\\
\hspace{1em}aorsf\_net & 0.741 (0.022) & 0.062 (0.049) & 585.625 & 126.3 & 585.887 & 114.7\\
\hspace{1em}Rfsrc & 0.707 (0.005) & 0.049 (0.039) & 1.354 & 0.292 & 1.522 & 0.298\\

@@

\hspace{1em}Rfsrc & 0.815 (0.007) & 0.279 (0.007) & 1.854 & 0.581 & 2.026 & 0.600\\
\hspace{1em}aORSF(i=15) & 0.778 (0.007) & 0.199 (0.018) & 7.515 & 2.36 & 7.709 & 2.28\\
\hspace{1em}aORSF(i=1) & 0.776 (0.004) & 0.201 (0.014) & 3.190 & 1.00 & 3.378 & 1.00\\
\hspace{1em}aorsf\_net & 0.753 (0.006) & 0.156 (0.018) & 149.637 & 46.9 & 149.809 & 44.3\\
\hspace{1em}Party & 0.753 (0.012) & 0.183 (0.008) & 3.968 & 1.24 & 10.451 & 3.09\\
\hspace{1em}Ranger & 0.738 (0.008) & 0.147 (0.005) & 1.795 & 0.563 & 2.398 & 0.710\\

@@

\hspace{1em}Ranger & 0.704 (0.076) & 0.090 (0.045) & 0.328 & 0.339 & 0.450 & 0.438\\
\hspace{1em}Party & 0.686 (0.042) & 0.092 (0.048) & 0.746 & 0.773 & 2.055 & 2.00\\
\hspace{1em}aORSF(i=15) & 0.685 (0.048) & 0.077 (0.066) & 2.077 & 2.15 & 2.144 & 2.09\\
\hspace{1em}Rfsrc & 0.676 (0.032) & 0.067 (0.052) & 0.931 & 0.963 & 1.014 & 0.986\\
\hspace{1em}aORSF(i=1) & 0.674 (0.045) & 0.062 (0.062) & 0.966 & 1.00 & 1.028 & 1.00\\
\hspace{1em}aorsf\_net & 0.670 (0.038) & 0.068 (0.056) & 57.024 & 59.0 & 57.087 & 55.5\\

@@

\hspace{1em}aORSF(i=15) & 0.730 (0.009) & 0.133 (0.008) & 4.705 & 2.67 & 4.811 & 2.57\\
\hspace{1em}aORSF(i=1) & 0.728 (0.014) & 0.132 (0.012) & 1.762 & 1.00 & 1.869 & 1.00\\
\hspace{1em}aorsf\_net & 0.728 (0.020) & 0.133 (0.015) & 86.476 & 49.1 & 86.590 & 46.3\\
\hspace{1em}Party & 0.705 (0.021) & 0.101 (0.010) & 1.800 & 1.02 & 3.727 & 1.99\\
\hspace{1em}Rfsrc & 0.705 (0.032) & 0.109 (0.027) & 1.000 & 0.568 & 1.104 & 0.591\\
\hspace{1em}Ranger & 0.704 (0.016) & 0.102 (0.001) & 0.663 & 0.376 & 0.855 & 0.457\\

@@

\hspace{1em}aORSF(i=1) & 0.787 (0.094) & 0.202 (0.188) & 2.204 & 1.00 & 2.400 & 1.00\\
\hspace{1em}aORSF(i=15) & 0.787 (0.100) & 0.203 (0.186) & 5.038 & 2.29 & 5.242 & 2.18\\
\hspace{1em}Ranger & 0.783 (0.091) & 0.161 (0.138) & 0.709 & 0.322 & 1.053 & 0.438\\
\hspace{1em}aorsf\_net & 0.782 (0.101) & 0.190 (0.202) & 128.300 & 58.2 & 128.469 & 53.5\\
\hspace{1em}Party & 0.779 (0.094) & 0.185 (0.167) & 3.291 & 1.49 & 6.998 & 2.92\\
\hspace{1em}Rfsrc & 0.778 (0.113) & 0.195 (0.187) & 0.956 & 0.434 & 1.076 & 0.448\\

>>>>

\subsection{Axis-based and oblique random forests}

After \citet{breiman2001random} introduced the axis-based and oblique random forest (RF), numerous methods were developed to grow oblique RFs for classification or regression tasks \citep{menze2011oblique, zhang2014oblique, rainforth2015canonical, zhu2015reinforcement, poona2016investigating, qiu2017oblique, tomita2020sparse, katuwal2020heterogeneous}. However, oblique splitting approaches for classification or regression may not generalize to survival tasks \citep[\eg, see][Section~4.5.1]{zhu2013tree}, and most research involving the RSF has focused on forests with axis-based trees \citep{wang2017selective}.

Building on prior research for bagging survival trees \citep{hothorn2004bagging}, \citet{hothorn2006unbiased} developed an axis-based RSF in their framework for unbiased recursive partitioning, more commonly referred to as the conditional inference forest (CIF). \citet{zhou2016random} developed a rotation forest based on the CIF and \citet{wang2017random} developed a method for extending the predictor space of the CIF. \citet{ishwaran2008random} developed an axis-based RSF with strict adherence to the rules for growing trees proposed in \citet{breiman2001random}. \citet{jaeger2019oblique} developed the oblique RSF following the bootstrapping approach described in Breiman's original RF and incorporating early stopping rules from the CIF.

\subsection{Variable importance}

\citet{breiman2001random} introduced permutation VI, defined for each predictor as the difference in a RF's estimated generalization error before versus after the predictor's values are randomly permuted. \citet{strobl2007bias} identified bias in permutation VI driven by variable selection bias and effects induced by bootstrap sampling, and proposed an unbiased permutation VI based on unbiased recursive partitioning (see \citet{hothorn2006unbiased}). \citet{menze2011oblique} introduced an approach to estimate VI for oblique RFs that computes an analysis of variance (ANOVA) table in non-leaf nodes to obtain p-values for each predictor contributing to the node. The ANOVA VI\footnote{\citet{menze2011oblique} name their method `oblique RF VI', but we use the name `ANOVA VI' in this article to avoid confusing Menze's approach with other approaches to estimate VI for oblique RFs.} is then defined for each predictor as the number of times a p-value associated with the predictor is $\leq 0.01$ while growing a forest. \citet{lundberg2017unified} introduced a method to estimate VI using SHapley Additive exPlanation (SHAP) values, which estimate the contribution of a predictor to a model's prediction for a given observation. SHAP VI is computed for each predictor by taking the mean absolute value of SHAP values for that predictor across all observations in a given set.

% Several supervised learning algorithms can develop prediction functions for right-censored time-to-event outcomes, henceforth referred to as survival outcomes. \cite{ishwaran2008random} developed the RF for survival, an extension of the RF for regression and classification developed by \citet{breiman2001random}. Fast algorithms to fit the RF for survival are available in the \texttt{randomForestSRC} R package \citep{randomForestSRC}. A similar implementation of the RF for survival can be found in the \texttt{ranger} R package \citep{ranger}, which is particularly suited for high dimensional data. The RF for survival can also be fit using unbiased recursive partitioning \citep{cif} via the \texttt{party} R package \citep{hothorn2010party}.

\section{Novel techniques for oblique random survival forests}

Consider the usual framework for survival analysis with training data $$\dataset_{\text{train}} = \left\{ (T_i, \delta_i, \bm{x}_{i}) \right\}_{i=1}^{N_{\text{train}}}.$$ Here, $T_i$ is the event time if $\delta_i=1$ and last point of contact if $\delta_i=0$, and $\bm{x}_i$ is a vector of predictors values. Assuming there are no ties, let $t_1 < \, \ldots \, < t_m$ denote the $m$ unique event times in $\dataset_{\text{train}}$.

\subsection{Partial training at non-leaf nodes}

We propose to identify linear combinations of predictor variables in non-leaf nodes by applying Newton Raphson scoring to the partial likelihood function of the Cox regression model:
\begin{equation}\label{eqn:cox-partial-likelihood}
L(\bm\beta) = \prod_{i=1}^m \frac{e^{\bm{x}_{j(i)}^T \bm\beta}}{\sum_{j \in R_i} e^{\bm{x}_j^T \bm\beta}},
\end{equation}
where $R_i$ is the set of indices, $j$, with $T_j \geq t_i$ (i.e., those still at risk at time $t_i$), and $j(i)$ is the index of the observation for which an event occurred at time $t_i$. The \texttt{survival} package includes documentation that outlines how to complete this estimation procedure efficiently \citep[see][exact.nw]{therneau_survival_2022}. Briefly, a vector of estimated regression coefficients, $\hat{\beta}$, is updated in each step of the procedure based on its first derivative, $U(\hat{\beta})$, and second derivative, $H(\hat{\beta})$:
$$ \hat{\beta}^{k+1} =  \hat{\beta}^{k} + U(\hat{\beta} = \hat{\beta}^{k})\, H^{-1}(\hat{\beta} = \hat{\beta}^{k}) $$
It is vital to cycle through iterations until a convergence threshold is met for statistical inference, but it is only necessary to complete one iteration to identify coefficients for a linear combination of predictors. \citet{jaeger2019oblique} identified linear combinations using penalized regression models, which supply more flexible solutions for $\hat{\beta}$ at the cost of greater computational demand.

\subsection{Negation variable importance}

Negation VI is similar to permutation VI in that it measures how much a model’s prediction error increases when a variable’s role in the model is de-stabilized. More specifically, negation VI measures the increase in an oblique RF's prediction error after flipping the sign of all coefficients linked to a variable (\ie, negating them). As the magnitude of a coefficient increases, so does the probability that negating it will change the oblique RF's predictions. Since the coefficients in each non-leaf node of an oblique RFs are adjusted for the accompanying predictors, negation VI may provide better estimation of VI in the presence of correlated variables compared to standard VI techniques. Although the current article focuses on oblique RSFs, negation VI can be applied to any oblique RF.

\section{Numeric experiments}

\subsection{Benchmark of prediction accuracy}

\subsubsection{Learners}

We consider four classes of learners: RFs, boosting ensembles, regression models, and neural networks (Table \ref{table:learners}). For RF learners, the number of observations required in terminal nodes was fixed at 10, the number of randomly selected predictors was the square root of the total number of predictors rounded to the nearest integer, and the number of trees in the ensemble was 500. For boosting, regression, and neural network learners, nested cross-validation was applied to tune each model, \ie, assess multiple possible values for relevant model parameters and use the values that optimize the model's estimated prediction accuracy. Specifically, tuning for boosting models included identifying the number of steps to complete. For regression models, tuning was used to identify the magnitude of penalization. For neural networks, the number and density of layers was tuned.

\newgeometry{margin=1cm} % modify this if you need even more space
\begin{landscape}

\begin{table}[h!]
\centering
\begin{tabular}{p{2cm} | p{3cm} p{4cm} p{12cm}}
 \hline
 Learner Class & Software & Learners & Description \\ [0.5ex]
 \hline\hline
 \multicolumn{3}{l}{\textit{Random Survival Forests}}\\
 \hline\hline

 Axis based &

 \href{https://www.randomforestsrc.org/index.html}{\texttt{RandomForestSRC}} \newline
 \href{https://CRAN.R-project.org/package=ranger}{\texttt{ranger}} \newline
 \href{http://party.r-forge.r-project.org/}{\texttt{party}} \newline
 \href{https://github.com/whcsu/rotsf}{\texttt{rotsf}} \newline
 \href{https://github.com/whcsu/rsfse}{\texttt{rsfse}} &

 \texttt{rsf-standard} \newline
 \texttt{rsf-extratrees} \newline
 \texttt{cif-standard} \newline
 \texttt{cif-rotate} \newline
 \texttt{cif-spacextend} &

 \texttt{rsf-standard} grows survival trees following Leo Breiman's original random forest algorithm with variables and cut-points selected to maximize a log-rank statistic. \texttt{rsf-extratrees} grows survival trees with randomly selected features and cut-points. \texttt{cif-standard} uses the framework of conditional inference to grow survival trees. \texttt{cif-rotate} extends \texttt{cif-standard} by applying principal component analysis to random subsets of data prior to growing each survival tree. \texttt{cif-spacextend} derives new predictors for each tree in the ensemble, separately. \\ \hline

 Oblique &

 \href{https://CRAN.R-project.org/package=obliqueRSF}{\texttt{obliqueRSF}} \newline
 \href{https://bcjaeger.github.io/aorsf/}{\texttt{aorsf}} &

 \texttt{obliqueRSF-net} \newline
 \texttt{aorsf-net} \newline
 \texttt{aorsf-fast} \newline
 \texttt{aorsf-cph} \newline
 \texttt{aorsf-extratrees} &

 Oblique survival trees following Leo Breiman's random forest algorithm. Linear combinations of inputs are derived using \texttt{glmnet} in \texttt{obliqueRSF-net} and \texttt{aorsf-net}, using Newton Raphson scoring for the Cox partial likelihood function in \texttt{aorsf-fast} and \texttt{aorsf-cph}, and chosen randomly from a uniform distribution in \texttt{aorsf-extratrees}. Cut-points are selected to maximize a log-rank statistic. \\

 \hline\hline
 \multicolumn{3}{l}{\textit{Boosting ensembles}}\\
 \hline\hline

 Trees &

 \href{https://xgboost.readthedocs.io/en/stable/#}{\texttt{xgboost}} &

 \texttt{xgboost-cox} \newline
 \texttt{xgboost-aft} &

 \texttt{xgboost-cox} maximizes the Cox partial likelihood function, whereas \texttt{xgboost-aft} maximizes the accelerated failure time likelihood function. Nested cross validation (5 folds) is applied to tune the number of trees grown, the minimum number of observations in a leaf node was 10, the maximum depth of trees was 6, and $\sqrt{p}$ variables were considered randomly for each tree split, where $p$ is the total number of predictors. \\
 \hline\hline
 \multicolumn{3}{l}{\textit{Regression models}}\\
 \hline\hline
 Cox Net & \texttt{glmnet} & \texttt{glmnet-cox} & The Cox proportional hazards model is fit using an elastic net penalty. Nested cross validation (5 folds) is applied to tune penalty terms.\\
 \hline\hline
 \multicolumn{3}{l}{\textit{Neural networks}}\\
 \hline\hline
 Cox Time & \href{https://raphaels1.github.io/survivalmodels/}{\texttt{survivalmodels}} & \texttt{nn-cox} & A neural network based on the proportional hazards model with time-varying effects. Nested cross-validation was applied to select the number of layers (from 1 to 8), the number of nodes in each layer (from $\sqrt{p}$/2 to $\sqrt{p}$), and the number of epochs to complete (up to 500). A drop-out rate of 10\% was applied during training.   \\
 \hline
\end{tabular}
\caption{Learning algorithms assessed in numeric studies}
\label{table:learners}
\end{table}

\end{landscape}
\restoregeometry

\subsubsection{Evaluation of prediction accuracy} \label{sec:prediction_accuracy}

Our primary metric for evaluating the accuracy of predicted risk is the integrated and scaled Brier score \citep{graf1999assessment}. For observation $i$ in the testing data, let $\widehat{S}(t \mid \bm{x}_i)$ be the predicted probability of survival up to a given prediction horizon of $t > 0$ and let $\bm{x}_i$ be the vector of predictor values. Define \begin{align*}
\bstat = \frac{1}{\ntest} \sum_{i=1}^{\ntest} &\{ \widehat{S}(t \mid \bm{x}_i)^2 \cdot I(T_i \leq t, \delta_i = 1) \cdot \widehat{G}(T_i)^{-1} \\ &+ [1-\widehat{S}(t \mid \bm{x}_i)]^2 \cdot I(T_i > t) \cdot \widehat{G}(t)^{-1}\}
\end{align*} where $\widehat{G}(t)$ is the Kaplan-Meier estimate of the censoring distribution. As $\bstat$ is time dependent, integration over time provides a summary measure of performance over a range of plausible prediction horizons. The integrated $\bstat$ is defined as \begin{equation}
\bsbar = \frac{1}{t_2 - t_1}\int_{t_1}^{t_2} \widehat{\text{BS}}(t) dt.
\end{equation} In our results, $t_1$ and $t_2$ are the 25th and 75th percentile of event times, respectively. $\bsbar$, a sum of squared prediction errors, can be scaled to produce a measure of explained residual variation (\ie, an $R^2$ statistic) by computing \begin{equation}
R^2 = 1 - \frac{\bsbar}{\bskap}
\end{equation} where $\bskap$ is the integrated Brier score when a Kaplan-Meier estimate for survival based on the training data is used as the survival prediction function $\widehat{S}(t)$. We refer to this $R^2$ statistic as the index of prediction accuracy and we scale its values by 100 to avoid unnecessary leading zero's. For example, we present 25 if $R^2$ is 0.25 and present 10.2 if the difference between two $R^2$ is 0.102.

\subsubsection{Statistical analysis}

\subsubsection{Results}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/unnamed-chunk-2-1} 
\end{knitrout}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/unnamed-chunk-3-1} 
\end{knitrout}

\subsection{Benchmark of variable selection}

\acks{Research reported in this publication was supported by the Center for Biomedical Informatics, Wake Forest University School of Medicine}

\appendix
\section*{Appendix A.}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/unnamed-chunk-4-1} 
\end{knitrout}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\begin{longtable}{lcclccl}
\toprule
\multicolumn{3}{c}{ } & \multicolumn{4}{c}{Computing time, seconds} \\
\cmidrule(l{3pt}r{3pt}){4-7}
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Performance metric (SD)} & \multicolumn{2}{c}{Fit model} & \multicolumn{2}{c}{Predict risk} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7}
  & Scaled Brier & C-Statistic & Median & Ratio & Median & Ratio\\
\midrule
\endfirsthead
\multicolumn{7}{@{}l}{\textit{(continued)}}\\
\toprule
  & Scaled Brier & C-Statistic & Median & Ratio & Median & Ratio\\
\midrule
\endhead

@@

\hspace{1em}aorsf-cph & 0.133 (0.124) & 0.757 (0.079) & 0.830 & 2.74 & 0.070 & 0.980\\
\hspace{1em}aorsf-fast & 0.133 (0.124) & 0.757 (0.080) & 0.302 & 1.00 & 0.072 & 1.00\\
\hspace{1em}aorsf-net & 0.130 (0.127) & 0.755 (0.080) & 61.237 & 202.6 & 0.069 & 0.964\\
\hspace{1em}cif-rotate & 0.125 (0.145) & 0.741 (0.092) & 30.623 & 101.3 & 7.208 & 100.3\\
\hspace{1em}cif-standard & 0.120 (0.111) & 0.748 (0.079) & 2.035 & 6.73 & 5.128 & 71.3\\
\hspace{1em}glmnet-cox & 0.119 (0.139) & 0.748 (0.083) & 0.253 & 0.837 & 0.005 & 0.070\\
\hspace{1em}rsf-standard & 0.118 (0.128) & 0.741 (0.084) & 1.694 & 5.60 & 0.152 & 2.11\\
\hspace{1em}obliqueRSF-net & 0.117 (0.094) & 0.754 (0.080) & 328.883 & 1,087.9 & 26.636 & 370.5\\
\hspace{1em}cif-extension & 0.108 (0.108) & 0.746 (0.083) & 13.510 & 44.7 & 6.840 & 95.2\\
\hspace{1em}ranger-extratrees & 0.106 (0.097) & 0.748 (0.076) & 0.692 & 2.29 & 0.264 & 3.68\\
\hspace{1em}aorsf-random & 0.101 (0.092) & 0.735 (0.074) & 1.879 & 6.22 & 0.066 & 0.919\\
\hspace{1em}xgboost-cox & 0.077 (0.114) & 0.736 (0.095) & 3.833 & 12.7 & 0.005 & 0.070\\
\hspace{1em}nn-cox & 0.030 (0.118) & 0.610 (0.128) & 15.427 & 51.0 & 1.513 & 21.0\\
\hspace{1em}xgboost-aft & -3.68 (4.86) & 0.747 (0.082) & 13.182 & 43.6 & 0.008 & 0.117\\

@@

\hspace{1em}aorsf-random & 0.028 (0.022) & 0.748 (0.038) & 0.637 & 4.19 & 0.040 & 1.06\\
\hspace{1em}ranger-extratrees & 0.028 (0.017) & 0.740 (0.036) & 0.061 & 0.404 & 0.184 & 4.81\\
\hspace{1em}obliqueRSF-net & 0.027 (0.022) & 0.746 (0.038) & 27.286 & 179.6 & 15.729 & 411.6\\
\hspace{1em}aorsf-cph & 0.025 (0.029) & 0.751 (0.042) & 0.450 & 2.97 & 0.034 & 0.891\\
\hspace{1em}cif-standard & 0.024 (0.031) & 0.744 (0.040) & 1.608 & 10.6 & 4.825 & 126.3\\
\hspace{1em}aorsf-fast & 0.024 (0.028) & 0.745 (0.044) & 0.152 & 1.00 & 0.038 & 1.00\\
\hspace{1em}cif-extension & 0.023 (0.015) & 0.722 (0.038) & 9.788 & 64.4 & 4.595 & 120.2\\
\hspace{1em}aorsf-net & 0.019 (0.034) & 0.745 (0.042) & 20.231 & 133.2 & 0.038 & 0.995\\
\hspace{1em}glmnet-cox & 0.016 (0.030) & 0.746 (0.037) & 0.183 & 1.21 & 0.002 & 0.053\\
\hspace{1em}rsf-standard & 0.005 (0.041) & 0.730 (0.042) & 0.235 & 1.55 & 0.071 & 1.85\\
\hspace{1em}cif-rotate & 0.004 (0.040) & 0.731 (0.038) & 15.089 & 99.3 & 4.246 & 111.1\\
\hspace{1em}xgboost-cox & 0.000 (0.044) & 0.751 (0.033) & 3.655 & 24.1 & 0.003 & 0.079\\
\hspace{1em}nn-cox & 0.000 (0.013) & 0.574 (0.117) & 12.345 & 81.3 & 0.639 & 16.7\\
\hspace{1em}xgboost-aft & -8.40 (1.81) & 0.737 (0.035) & 11.029 & 72.6 & 0.007 & 0.183\\

@@

\hspace{1em}obliqueRSF-net & 0.007 (0.012) & 0.819 (0.051) & 9.302 & 102.7 & 10.943 & 545.1\\
\hspace{1em}aorsf-cph & 0.007 (0.019) & 0.815 (0.058) & 0.363 & 4.00 & 0.020 & 1.00\\
\hspace{1em}aorsf-fast & 0.006 (0.019) & 0.820 (0.054) & 0.091 & 1.00 & 0.020 & 1.00\\
\hspace{1em}aorsf-random & 0.004 (0.015) & 0.780 (0.070) & 0.326 & 3.60 & 0.026 & 1.30\\
\hspace{1em}ranger-extratrees & 0.001 (0.020) & 0.773 (0.071) & 0.045 & 0.497 & 0.143 & 7.13\\
\hspace{1em}cif-extension & 0.001 (0.021) & 0.759 (0.061) & 8.354 & 92.2 & 3.905 & 194.5\\
\hspace{1em}xgboost-cox & -0.004 (0.004) & 0.500 (0.000) & 0.120 & 1.32 & 0.002 & 0.100\\
\hspace{1em}nn-cox & -0.004 (0.004) & 0.535 (0.110) & 11.322 & 125.0 & 0.689 & 34.3\\
\hspace{1em}cif-standard & -0.006 (0.026) & 0.773 (0.056) & 1.758 & 19.4 & 4.361 & 217.2\\
\hspace{1em}aorsf-net & -0.006 (0.033) & 0.799 (0.065) & 15.227 & 168.1 & 0.025 & 1.25\\
\hspace{1em}rsf-standard & -0.031 (0.053) & 0.769 (0.069) & 0.090 & 0.994 & 0.038 & 1.90\\
\hspace{1em}cif-rotate & -0.037 (0.052) & 0.704 (0.094) & 13.476 & 148.8 & 3.663 & 182.5\\
\hspace{1em}glmnet-cox & -0.062 (0.092) & 0.736 (0.098) & 0.301 & 3.33 & 0.001 & 0.051\\
\hspace{1em}xgboost-aft & -24.3 (7.36) & 0.767 (0.066) & 10.846 & 119.7 & 0.008 & 0.399\\

@@

\hspace{1em}aorsf-fast & 0.100 (0.014) & 0.718 (0.011) & 0.289 & 1.00 & 0.075 & 1.00\\
\hspace{1em}aorsf-cph & 0.100 (0.014) & 0.717 (0.011) & 0.691 & 2.39 & 0.070 & 0.945\\
\hspace{1em}cif-standard & 0.097 (0.013) & 0.710 (0.012) & 1.529 & 5.29 & 5.019 & 67.4\\
\hspace{1em}aorsf-net & 0.097 (0.014) & 0.717 (0.012) & 55.870 & 193.4 & 0.064 & 0.853\\
\hspace{1em}aorsf-random & 0.096 (0.010) & 0.716 (0.011) & 1.612 & 5.58 & 0.066 & 0.879\\
\hspace{1em}obliqueRSF-net & 0.089 (0.006) & 0.717 (0.012) & 269.561 & 932.9 & 44.243 & 593.8\\
\hspace{1em}cif-rotate & 0.087 (0.017) & 0.705 (0.014) & 15.603 & 54.0 & 6.291 & 84.4\\
\hspace{1em}rsf-standard & 0.087 (0.019) & 0.704 (0.011) & 1.646 & 5.70 & 0.143 & 1.92\\
\hspace{1em}ranger-extratrees & 0.083 (0.007) & 0.710 (0.011) & 0.735 & 2.54 & 0.263 & 3.53\\
\hspace{1em}cif-extension & 0.081 (0.006) & 0.709 (0.011) & 8.523 & 29.5 & 5.850 & 78.5\\
\hspace{1em}glmnet-cox & 0.076 (0.016) & 0.711 (0.019) & 0.132 & 0.457 & 0.004 & 0.054\\
\hspace{1em}xgboost-cox & 0.063 (0.013) & 0.701 (0.013) & 3.266 & 11.3 & 0.004 & 0.054\\
\hspace{1em}nn-cox & -0.013 (0.040) & 0.506 (0.042) & 14.970 & 51.8 & 1.780 & 23.9\\
\hspace{1em}xgboost-aft & -1.11 (0.200) & 0.706 (0.013) & 12.660 & 43.8 & 0.007 & 0.094\\

@@

\hspace{1em}aorsf-fast & 0.100 (0.017) & 0.713 (0.016) & 0.282 & 1.00 & 0.069 & 1.00\\
\hspace{1em}aorsf-cph & 0.099 (0.017) & 0.712 (0.016) & 0.708 & 2.52 & 0.070 & 1.01\\
\hspace{1em}aorsf-net & 0.096 (0.018) & 0.713 (0.017) & 51.056 & 181.3 & 0.065 & 0.937\\
\hspace{1em}cif-standard & 0.091 (0.015) & 0.701 (0.017) & 1.183 & 4.20 & 4.109 & 59.2\\
\hspace{1em}obliqueRSF-net & 0.088 (0.008) & 0.711 (0.015) & 298.417 & 1,059.9 & 44.698 & 643.9\\
\hspace{1em}aorsf-random & 0.087 (0.012) & 0.703 (0.015) & 1.629 & 5.78 & 0.064 & 0.923\\
\hspace{1em}cif-rotate & 0.084 (0.020) & 0.695 (0.017) & 14.130 & 50.2 & 6.064 & 87.4\\
\hspace{1em}cif-extension & 0.082 (0.009) & 0.707 (0.017) & 8.587 & 30.5 & 6.571 & 94.7\\
\hspace{1em}rsf-standard & 0.081 (0.020) & 0.694 (0.015) & 1.408 & 5.00 & 0.139 & 2.00\\
\hspace{1em}ranger-extratrees & 0.079 (0.011) & 0.700 (0.016) & 0.555 & 1.97 & 0.235 & 3.39\\
\hspace{1em}glmnet-cox & 0.073 (0.018) & 0.706 (0.024) & 0.161 & 0.572 & 0.005 & 0.072\\
\hspace{1em}xgboost-cox & 0.060 (0.011) & 0.695 (0.018) & 3.088 & 11.0 & 0.004 & 0.058\\
\hspace{1em}nn-cox & -0.005 (0.005) & 0.506 (0.039) & 13.814 & 49.1 & 1.499 & 21.6\\
\hspace{1em}xgboost-aft & -1.20 (0.239) & 0.701 (0.019) & 11.979 & 42.5 & 0.007 & 0.101\\

@@

\hspace{1em}obliqueRSF-net & 0.073 (0.024) & 0.749 (0.027) & 1951.148 & 2,519.7 & 15.143 & 83.8\\
\hspace{1em}cif-rotate & 0.072 (0.017) & 0.748 (0.027) & 6765.191 & 8,736.4 & 351.642 & 1,947.0\\
\hspace{1em}cif-standard & 0.068 (0.018) & 0.745 (0.029) & 8.817 & 11.4 & 4.397 & 24.3\\
\hspace{1em}cif-extension & 0.066 (0.014) & 0.746 (0.025) & 45.390 & 58.6 & 6.577 & 36.4\\
\hspace{1em}aorsf-cph & 0.065 (0.031) & 0.745 (0.024) & 1.280 & 1.65 & 0.179 & 0.992\\
\hspace{1em}aorsf-fast & 0.063 (0.031) & 0.744 (0.024) & 0.774 & 1.00 & 0.181 & 1.00\\
\hspace{1em}ranger-extratrees & 0.061 (0.024) & 0.740 (0.028) & 0.224 & 0.290 & 0.180 & 0.997\\
\hspace{1em}glmnet-cox & 0.043 (0.034) & 0.723 (0.037) & 5.608 & 7.24 & 0.005 & 0.028\\
\hspace{1em}xgboost-cox & 0.040 (0.014) & 0.743 (0.026) & 2.236 & 2.89 & 0.007 & 0.039\\
\hspace{1em}aorsf-random & 0.030 (0.015) & 0.699 (0.036) & 1.847 & 2.38 & 0.190 & 1.05\\
\hspace{1em}rsf-standard & 0.020 (0.041) & 0.693 (0.033) & 0.382 & 0.493 & 0.666 & 3.69\\
